---
title: "Welcome to WILDS"
toc: false
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(bs)
library(bslib)
library(htmltools)

# from bslib docs
anim_width <- function(x, width1, width2) {
  x |> tagAppendAttributes(
    class = "animate-width",
    style = css(
      `--width1` = validateCssUnit(width1),
      `--width2` = validateCssUnit(width2),
    ),
  )
}
```

```{r fix-me-hack-to-include-fontawesome-css, echo=FALSE}
cat("{{< fa box-open >}}  ")
```

### The Open Source Software Office of the Fred Hutchinson Cancer Center

#### Our Mission

Open source software has allowed the biomedical data science community to 
flourish, and therefore to encourage open science practices and to cultivate
the development of open source software at Fred Hutch, the Data Science Lab 
(DaSL) created WILDS, the open source software office of the Fred Hutch Cancer 
Center. The mission of WILDS includes the following:

- Engage with the Cancer Consortium community about how they can adopt open
science practices into their own workflows.
- Educate our community about the critical role that open source software plays
in biomedical data science practice.
- Support open-source software developers across the Cancer Consortium.
- Elevate the quality of open-source software being developed at Fred Hutch.
- Empower new open-source developers by evangelizing best practices and
catalyzing community around the open-source software development process.
- Connect developers, researchers, and providers to opportunities to share,
academically publish, and publicize their software.
- Collaborate within the Fred Hutch community to build the next generation of
open source software tools.

#### Our Contribution

To support our mission, WILDS is actively engaged in the following activities:

- We maintain, distribute, and publish open source scientific software, mostly
implemented in the Python and R ecosystems.
- We maintain and distribute open source scientific workflows implemented in
WDL or Nextflow. 
- We develop [research compendia][rescomp] to demonstrate common data analyses
and how they can best be organized and shared.
- We package and develop Docker recipies and Dockerfiles so that researchers
can run pipelines in consistent computing environments.
- We create and maintain documentation about how to use and contribute to
WILDS resources.
- We co-sponsor and create materials for [DaSL's Community Studios][comm].

All of these open source resources are designed for researchers to either use
off-the-shelf or as tools and templates that they can adapt into their own work.
Click on any of the boxes below to explore the resources that WILDS has to 
offer.

<!-- <br><br> -->

{{< include cards.qmd >}}

# Code {.center1}

```{r code, echo=FALSE, results="asis"}
layout_column_wrap(
  width = "200px", height = 500,
  card_r, card_python, card_docker, card_comp, card_wdl, card_nf
) |>
  anim_width("100%", "67%")
```

<br>

# Get involved {.center1}

{{< fa circle-info >}} **Read** - [WILDS Contributor Guide][guide]

{{< fa hammer >}} **Contribute** - See our [projects page](projects.html)



[dasl]: https://hutchdatascience.org/
[guide]: https://getwilds.org/guide/
[comm]: https://hutchdatascience.org/communitystudios/
[rescomp]: https://research-compendium.science/