---
title: "Welcome to WILDS"
toc: false
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(bs)
library(bslib)
library(htmltools)

# from bslib docs
anim_width <- function(x, width1, width2) {
  x |> tagAppendAttributes(
    class = "animate-width",
    style = css(
      `--width1` = validateCssUnit(width1),
      `--width2` = validateCssUnit(width2),
    ),
  )
}
```

```{r fix-me-hack-to-include-fontawesome-css, echo=FALSE}
cat("{{< fa box-open >}}  ")
```

### The Open-Source Software Office of the Fred Hutchinson Cancer Center

#### Our Mission

In recognition of the fact that open source software is the engine of
biomedical data science, the Data Science Lab (DaSL) created WILDS, the 
open-source software office of the Fred Hutchinson Cancer Center. The 
mission of WILDS includes the following:

- Engage with people developing open-source software across the Cancer
Consortium.
- Elevate the quality of open-source software being developed at Fred Hutch.
- Empower new open-source developers by evangelizing best practices and
catalyzing community around the open-source software development process.
- Connect developers, researchers, and providers to opportunities to share,
academically publish, and publicize their software.
- Collaborate within the Fred Hutch community to build the next generation of
open-source software tools.

<br><br>

{{< include cards.qmd >}}

# Code {.center1}

```{r code, echo=FALSE, results="asis"}
layout_column_wrap(
  width = "200px", height = 500,
  card_r, card_python, card_docker, card_comp, card_wdl, card_nf
) |>
  anim_width("100%", "67%")
```

<br>

# Get involved {.center1}

{{< fa circle-info >}} **Read** - [WILDS Contributor Guide][guide]

{{< fa hammer >}} **Contribute** - See our [packages page](packages.html)



[dasl]: https://hutchdatascience.org/
[guide]: https://getwilds.org/guide/
